Slitasje og kjørespor

### 2023-01-19 DRAFT_slitasjeOgKjørespor.Rmd
doc: Some text, switching branches

This normalisation seems reasonable to me. I can save it as indicator
values. I will assign the indicator value to the average year of the
data.

@@

### Homogeneous impact areas
I want to use the [homogeneous impact areas]() (HIA) to define smaller regions into which I can extrapolate the indicator values.
This data is generated by discretizing the Norwegian Infrastructure Index. I refer to the ordinal values of the
four impact area classes as their *Human Impact Factor* (HIF).

@@

```{r, fig.cap="Counting the number of gridd cells for each Human Impact Factor."}
barplot(table(HIA$infrastructureIndex),
        ylab = "Number of 1x1 km grid cells",
        xlab = "Human impact factor")
```

>>>>

This normalisation seems reasonable to me. I can save it as indicator
values. There is no point yet making this a time series, and I will 
assign all the indicator value to the average year of the
data.

@@

### Homogeneous impact areas
I want to use the [Homogeneous Impact Areas] (HIA) to define smaller regions into which I can extrapolate the indicator values.
This data is generated by discretizing the Norwegian Infrastructure Index. I refer to the ordinal values of the
four impact area classes as their *Human Impact Factor* (HIF).

@@
